\bf Title here

### 2020-08-20 paper/paper.Rmd
change of subsection titles

## Global object

@@

## Plot definition

@@

### Explore searching points

@@

```{r toy-search, fig.height=5.5, fig.cap="\\label{toy-search}A comparison of plotting the same search points with different plot designs. In upper plot, points from the last three iteration spans the vast majority of the plotting space leaving the first few iterationsbeing squeezed together whilst the lower plot spaces each iteration evenly and present summary information easy to read."}

@@

### Explore interpolating points

@@

### Explore the searching space

@@

# Application {#application}

@@

>>>>

## Data structure

@@

## Plot constructions

@@

### How hard is the optimiser working

@@

```{r toy-search, fig.height=5.5, fig.cap="\\label{toy-search}A comparison of plotting the same search points with different plot designs. In upper plot, points from the last three iterations span the vast majority of the plotting space leaving the first few iterations being squeezed together whilst the lower plot spaces each iteration evenly and presents summary information easy to read."}

@@

### Examining the interpolation

@@

### Understanding the optimiser's coverage of the search space

@@

# Diagnosing an optimiser {#application}

[a paragraph that motivate the section: these optimisers are suspect to have problem, here is how we use the diag plot to diagnose them. ]

@@

## Simulation setup

### 2020-08-20 paper/paper.tex
change of subsection titles

\hypertarget{global-object}{%
\subsection{Global object}\label{global-object}}

@@

\hypertarget{plot-definition}{%
\subsection{Plot definition}\label{plot-definition}}

\hypertarget{explore-searching-points}{%
\subsubsection{Explore searching
points}\label{explore-searching-points}}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/toy-search-1.pdf}
\caption{\label{toy-search}A comparison of plotting the same search
points with different plot designs. In upper plot, points from the last
three iteration spans the vast majority of the plotting space leaving
the first few iterationsbeing squeezed together whilst the lower plot
spaces each iteration evenly and present summary information easy to
read.}
\end{figure}

@@

\hypertarget{explore-interpolating-points}{%
\subsubsection{Explore interpolating
points}\label{explore-interpolating-points}}

@@

\hypertarget{explore-the-searching-space}{%
\subsubsection{Explore the searching
space}\label{explore-the-searching-space}}

@@

\hypertarget{application}{%
\section{Application}\label{application}}

@@

>>>>

\hypertarget{data-structure}{%
\subsection{Data structure}\label{data-structure}}

@@

\hypertarget{plot-constructions}{%
\subsection{Plot constructions}\label{plot-constructions}}

\hypertarget{how-hard-is-the-optimiser-working}{%
\subsubsection{How hard is the optimiser
working}\label{how-hard-is-the-optimiser-working}}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/toy-search-1.pdf}
\caption{\label{toy-search}A comparison of plotting the same search
points with different plot designs. In upper plot, points from the last
three iterations span the vast majority of the plotting space leaving
the first few iterations being squeezed together whilst the lower plot
spaces each iteration evenly and presents summary information easy to
read.}
\end{figure}

@@

\hypertarget{examining-the-interpolation}{%
\subsubsection{Examining the
interpolation}\label{examining-the-interpolation}}

@@

\hypertarget{understanding-the-optimisers-coverage-of-the-search-space}{%
\subsubsection{Understanding the optimiser's coverage of the search
space}\label{understanding-the-optimisers-coverage-of-the-search-space}}

@@

\hypertarget{application}{%
\section{Diagnosing an optimiser}\label{application}}

{[}a paragraph that motivate the section: these optimisers are suspect
to have problem, here is how we use the diag plot to diagnose them. {]}

@@

\hypertarget{simulation-setup}{%
\subsection{Simulation setup}\label{simulation-setup}}
